---
title: "Intro to Statistics"
author: "Eric Miedema"
output: ioslides_presentation
---

## R Markdown

**Statistics** is the science of collecting, analyzing, and drawing conclusions from data

## Why

My backgroud... why are you taking this class?

##Course Logistics

### Content
- Syllabus  
- Slides for each unit on Moodle  
- Lecture notes and video on Moodle  
  
### Grades  
- 10%	Attendance and class participation
- 15%	Homework
- 15%	Exam I
- 15%	Exam II
- 15%	Exam III
- 30%	Final

## Data Science Community

### Public Galleries

- [Shiny Applications](http://shiny.rstudio.com/gallery/)
- [Tableau Dashboards](https://public.tableau.com/s/gallery)
- [Google Charts](https://developers.google.com/chart/)

### Open course examples

- [Coursera Data Science](https://www.coursera.org/specializations/jhu-data-science)
- [eDX Data Analysis](https://www.edx.org/xseries/data-analysis-life-sciences)

### Blogs and Sites
- [R Blogger](https://www.r-bloggers.com/)
- [Kaggle]([https://www.kaggle.com/)
- Others?  Let me know

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

