---
title: "Statistical Tables"
output: html_document
fontsize: 11
---

<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
  .col3 {
    columns: 2 100px;
    -webkit-columns: 2 100px;
    -moz-columns: 2 100px;
  }
  .pagebreak { page-break-before: always; }
</style>

###### T Critical Value

```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
library(googleVis)
op <- options(gvis.plot.tag='chart')
df<-c(1:30,40,60,120,10000)
CI<-data.frame(Degrees_of_freedom = df, 
               Conf.Lvl_80 = round(qt(.9,df),2),
               Conf.Lvl_90 = round(qt(.95,df),2),
               Conf.Lvl_95 = round(qt(.975,df),2),
               Conf.Lvl_98 = round(qt(.99,df),2),
               Conf.Lvl_99 = round(qt(.995,df),2),
               Conf.Lvl_99.9 = round(qt(.9995,df),2))
```

```{r echo = FALSE, warning=FALSE, message=FALSE, results='asis'}
Table <- gvisTable(CI)
plot(Table)
```

<div class="pagebreak"> </div>
###### T Tables (tail area to the right of t for degrees of freedom 1 through 15)
```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
library(googleVis)
op <- options(gvis.plot.tag='chart')
df<-c(1:15)
t_value<-c(0:40)/10

for(i in seq_along(df)){
  if(i == 1){ a<-round(pt(t_value,df[i],lower.tail = FALSE),3)}
  else{a<-cbind(a,round(pt(t_value,df[i],lower.tail = FALSE),3))}
}
colnames(a)<-as.character(df)
rownames(a)<-as.character(t_value)
a<-cbind(t_df = rownames(a),a)
df<-data.frame(a)
```

```{r echo = FALSE, warning=FALSE, message=FALSE, results='asis'}
Table <- gvisTable(df)
plot(Table)
```

<div class="pagebreak"> </div>
###### T Tables (tail area to the right of t for degrees of freedom 16 through 30)
```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
library(googleVis)
op <- options(gvis.plot.tag='chart')
df<-c(16:30)
t_value<-c(0:40)/10

for(i in seq_along(df)){
  if(i == 1){ a<-round(pt(t_value,df[i],lower.tail = FALSE),3)}
  else{a<-cbind(a,round(pt(t_value,df[i],lower.tail = FALSE),3))}
}
colnames(a)<-as.character(df)
rownames(a)<-as.character(t_value)
a<-cbind(t_df = rownames(a),a)
df<-data.frame(a)
```

```{r echo = FALSE, warning=FALSE, message=FALSE, results='asis'}
Table <- gvisTable(df)
plot(Table)
```

<div class="pagebreak"> </div>
###### T Tables (tail area to the right of t for large degrees of freedom)
```{r echo = FALSE, warning=FALSE, message=FALSE, results='hide'}
library(googleVis)
op <- options(gvis.plot.tag='chart')
df<-c(30,35,40,45,50,60,70,80,90,100,120,120,10000)
t_value<-c(0:40)/10

for(i in seq_along(df)){
  if(i == 1){ a<-round(pt(t_value,df[i],lower.tail = FALSE),3)}
  else{a<-cbind(a,round(pt(t_value,df[i],lower.tail = FALSE),3))}
}
colnames(a)<-as.character(df)
rownames(a)<-as.character(t_value)
a<-cbind(t_df = rownames(a),a)
df<-data.frame(a)
```

```{r echo = FALSE, warning=FALSE, message=FALSE, results='asis'}
Table <- gvisTable(df)
plot(Table)
```